To Do List

### 2019-08-01 Papers.Rmd
Add 3DEpiLoop paper

>>>>

- Al Bkhetan, Ziad, and Dariusz Plewczynski. “Three-Dimensional Epigenome Statistical Model: Genome-Wide Chromatin Looping Prediction.” Scientific Reports 8, no. 1 (December 2018). https://doi.org/10.1038/s41598-018-23276-8. - 3DEpiLoop - prediction of 3D interactions from 1D epigenomic profiles using Random Forest trained on CTCF peaks (histone modifications are the most important predictors, and TFBSs). https://bitbucket.org/4dnucleome/3depiloop
